---
title: "Experimental Stimuli: Jern et al. (2014) Replication"
author: "Victor Moreno"
bibliography: ../references.bib
format: html
---

## Overview 

In this notebook, I recreate the two versions of the frequency chart used in all three conditions of the present replication. As in @jern2014, all participants see the same chart on both screen 1 and screen 2. Participants are informed that the chart shows the number of previous patients (out of 1,000) diagnosed with each of the four diseases.

The proportions come from the cover story template provided by Dr. Alan Jern (personal communication, 2026). All analyses are conducted in R [@R2025]


## Setup
```{r}
## Proportions from Dr. Alan Jern's cover story template
df1 <- data.frame(
  disease = c("L1", "L2", "Y1", "Y2"),
  count = c(10, 350, 240, 400), ## counts out of 1,000 to match original paper's y-axis framing 
  class = c("Allozedic","Allozedic", "Hypozedic", "Hypozedic")
  )

## Specify order to ensure consistency with the chart from the original paper
df1$disease <- factor(df1$disease, 
                     levels = c("L1", "L2", "Y1", "Y2"))
df2 <- df1 ## data differs only in disease class assignments
df2$class <- ifelse(df1$class == "Allozedic", "Hypozedic", "Allozedic")

```

## Plot creation
```{r}
library(ggplot2)

## Plot 1: Hypozedic as the more frequently occuring disease class. 
plot1 <- ggplot(df1, aes(x = disease, y = count, fill = class)) +
  geom_bar(stat = "identity",
           width = 0.6,
           color = "black",
           linewidth = 0.3) +
 scale_fill_manual(values = c("Allozedic" = "#4A90D9", 
                              "Hypozedic" = "#E87040"),
                   breaks = c("Allozedic", "Hypozedic"))+
  scale_y_continuous(limits = c(0, 500), 
                     breaks = seq(0, 500, 100),
                     expand = c(0, 0)) +
  labs(
    x = "",
    y = "Number of people",
    fill = ""
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    legend.position = "top",
    legend.justification = "center",
    panel.grid.major.y = element_line(color = "grey90", linewidth = 0.3)
  )
plot1

## Plot 2: Allozedic as the more frequently occuring disease class. 
plot2 <- ggplot(df2, aes(x = disease, y = count, fill = class)) +
  geom_bar(stat = "identity",
           width = 0.6,
           color = "black",
           linewidth = 0.3) +
  scale_fill_manual(values = c("Allozedic" = "#4A90D9", 
                              "Hypozedic" = "#E87040"),
                  breaks = c("Hypozedic", "Allozedic"))+
  scale_y_continuous(limits = c(0, 500), 
                     breaks = seq(0, 500, 100),
                     expand = c(0, 0)) +
  labs(
    x = "",
    y = "Number of people",
    fill = ""
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    legend.position = "top",
    legend.justification = "center",
    panel.grid.major.y = element_line(color = "grey90", linewidth = 0.3)
  )
plot2
```

## Export plots
```{r}
ggsave("../materials/chart_hypozedic.png", 
       plot = plot1,
       width = 6, 
       height = 4, 
       dpi = 300)
ggsave("../materials/chart_allozedic.png", 
       plot = plot2,
       width = 6, 
       height = 4, 
       dpi = 300)
```

