---
title: "Data Processing: Jern et al. (2014) Replication"
author: "Victor Moreno"
bibliography: ../references.bib
format: html
---

## Overview 

In this notebook, I load experimental data exported from Qualtrics as a CSV file and restructure it to match the expected format of my analyses pipeline. I then export the processed data as a new CSV file. All analyses are conducted in R [@R2025], following the approaches outlined in @frank2025experimentology.

## Import and examine data
```{r}

library(tidyverse)
df <- read_csv("../data/raw/JernRep-Data-Raw-Pilot.csv")
df |> head(10)

```
## Subset for relevant columns from unique & completed administrations only
```{r}
df <- df |> 
  slice(-c(1:2)) |> ## Drop metadata
  select(c('Finished',
           'PROLIFIC_PID',
           'DistributionChannel',
           'ResponseId',
           'Condition',
           'Disease',
           'Test1Text',
           'Test2Text',
           'Q1H_1',
           'Q2H',
           'Q3H_1',
           'Q1A_1',
           'Q2A',
           'Q3A_1',
           'TestOrder',
           'Duration (in seconds)',
           )) |> 
  filter(Finished == 1, ## Filter for completed administrations
         ## Filter for non-QualtricsGenerated administrations
         DistributionChannel == 'anonymous',
         PROLIFIC_PID != '{{%TEST123%}}') |> 
  distinct(PROLIFIC_PID, .keep_all = TRUE) |> ## Filter for unique response IDs
  select(-c('Finished', 'DistributionChannel'))

df |> head(10)
```
## Rename and restructure columns for readability   
```{r}
library(stringr)
df <- df |>
  rename_with(~ str_replace_all(.x, "[-_]", "")) |> ## Tidy up column names
  rename(Duration = `Duration (in seconds)`,
         Q1H = Q1H1,
         Q3H = Q3H1,
         Q1A = Q1A1,
         Q3A = Q3A1) |>
  mutate(across(Condition:Test2Text, as.factor), ## Convert variable types
         across(Q1H:Q3A, as.numeric),
         TestOrder = factor(TestOrder),
         Duration = as.numeric(Duration),
         Initial = coalesce(Q1H, Q1A), ## Collapse across disease groups 
         Final = coalesce(Q3H, Q3A),
         ChoiceRaw = coalesce(Q2H, Q2A),
         ChoiceText = case_when(
           ChoiceRaw == 1 ~ Test1Text,
           ChoiceRaw == 2 ~ Test2Text
         ),
         ## Choice should be set to 1 when the participant reported greater confidence in the test pointing to a disease associated with the class on the positive end of the scale, 0 if otherwise
         Choice = case_when(
            Condition %in% c("Polarization", "Moderation") & ChoiceText %in% c("Y1", "Y2") ~ 1, ## Y1 and Y2 are always associated with the disease group on the positive end of the scale 
            Condition %in% c("Polarization", "Moderation") ~ 0,
            Condition == "Control" & Disease == "H" & str_detect(ChoiceText, "hypozedic") ~ 1, 
            Condition == "Control" & Disease == "H" ~ 0,
            Condition == "Control" & Disease == "A" & str_detect(ChoiceText, "allozedic") ~ 1,
            Condition == "Control" & Disease == "A" ~ 0,
            TRUE ~ NA_real_
         )
         )
df |> head(10)
```

## Drop exclusions   
```{r}
## Filter for entries qualifying for exclusion & produce summary  
exclusions <- df |>
  filter(Initial < 0) 
  
## Drop participants whose initial response was skewed toward the disease class on the negative end of the scale
df <- df |>
  filter(Initial >= 0) 

cat(nrow(exclusions), "participants were excluded from subsequent analyses.\nAfter exclusions, N = ", nrow(df), ".")
```

## Classify participants based on absolute difference in certainty & flag those who crossed the scale's midpoint (0)
```{r}
df <- df |> 
  mutate(Delta = abs(Final) - abs(Initial), ## Absolute difference calculation
         CertaintyClass = case_when(Delta >= 5 ~ "More", ## Difference threshold set to +/- 5 
                                    Delta <= -5 ~ "Less",
                                    TRUE ~ "Equal"),
         CrossFlag = case_when((sign(Initial) != sign(Final)) & (Initial != 0) & (Final != 0 ) ~ 1, ## Flag administrations in which the participant's certainty crossed 0 
                               TRUE ~ 0)
  )
df |> head(10)
```

## Final check and data export
```{r}
## Final check
stopifnot(
  ## Confirm each participant answered exactly one question set 
  all(xor(!is.na(df$Q1H), !is.na(df$Q1A))),
  ## Confirm each participant has a non-NA value in the derived variable columns
  !any(is.na(df$Initial)),
  !any(is.na(df$Choice)),
  !any(is.na(df$Final)),
  !any(is.na(df$CertaintyClass)),
  !any(is.na(df$Choice)),
  ## Re-check for duplicate administrations
  !any(duplicated(df$ResponseId))
)

## Final select & export
df_processed <- df |>
  select(c('ResponseId',
           'Condition',
           'Disease',
           'Initial',
           'Choice',
           'Final',
           'Delta',
           'CertaintyClass',
           'CrossFlag',
           'TestOrder',
           'ChoiceRaw',
           'ChoiceText',
           'Duration'
           ))

write_csv(df_processed, '../data/processed/JernRep-Data-Processed-Pilot.csv')

```

