---
title: "Power Analysis: Jern et al. (2014) Replication"
author: "Victor Moreno"
bibliography: references.bib
format: html
---

## Overview

The study used a 3 (condition: polarization, moderation, control) x 2 (forced choice groups: yes, no) between-subjects design. The primary outcome was whether participants became less certain, equally certain, or more certain about their initial disease-class judgment after being presented with two contradictory test results. The primary comparisons of interest are Polarization vs. Control and Moderation vs. Control. 

In this notebook, I recover the proportions for the polarization and moderation conditions from the reported z-statistics and sample sizes, calculate Cohen's h for each comparison, and estimate the n per condition required to detect these effects at 80% power (@cohen1969). Total N is calculated by multiplying the n per group by 6 (3 conditions x 2 forced choice groups). Effect sizes are estimated from the no-forced choice group to yield a more conservative sample size estimate, given that it was associated with a smaller z-statistic than the forced choice group. 

## Reported statistics
```{r}

## Reported sample sizes per condition (no forced choice)
n_pol <- 87 ## polarization
n_mod <- 89 ## moderation
n_ctrl <- 86 ## control

## Reported proportions from control condition (no forced choice)
p_ctrl_more <- 0.20 ## proportion of participants in the control who became more certain 
p_ctrl_less <- 0.38 ## proportion of participants in the control who became less certain 
p_ctrl_equal <- 0.42 ## proportion of participants in the control who remained equally certain, not used in power analysis

## Reported z-statistics (one-tailed, no forced choice)
z_pol <- 2.18 ## polarization vs control, outcome = more certain 
z_mod <- 1.87 ## moderation vs control, outcome = less certain 

```

## Recover non-reported statistics 

The authors reported the relative proportion of participants in the control condition who were classified as less certain, equally certain, and more certain. However, to calculate the n per condition required to detect these effects at 80% power, we also need to recover the proportion of participants in these three categories in the polarization and moderation condition. 

To do so, we use the equation for one-tailed z-tests for proportions, plugging in p2 = control to find the value of p1 (polarization/moderation) where z(this p1) - z_reported = 0:
  z = (p1 - p2) / sqrt( p_pool * (1 - p_pool) * (1/n1 + 1/n2) ),
  p_pool =  (p1 * n1 + p2 * n2) / (n1 + n2)
```{r}
## recover p1
calc_p1 <- function(z_reported, p2, n1, n2) {
  eq <- function(p1){
    ## proportion pooled across conditions 
    p_pool <- (p1 * n1 + p2 * n2) / (n1 + n2)
    ## se of diff in proportions under the null
    se <- sqrt(p_pool * (1 - p_pool) * (1/n1 + 1/n2))
    ## z_reported subtracted from the z-statistic this p1 would produce
    ((p1-p2) / se) - z_reported
  }
  ## solve for p1 s.t this z(this p1) - z_reported = 0 
  result <- uniroot(eq, 
                    interval = c(p2, 0.99))
  ## output
  return(result$root)
}

## Polarization proportion (more certain)
p_pol_more <- calc_p1(
  z_reported = z_pol,
  p2 = p_ctrl_more, ## control 
  n1 = n_pol, ## polarization
  n2 = n_ctrl ## control
)

## Moderation proportion (less certain)
p_mod_less <- calc_p1(
  z_reported = z_mod,
  p2 = p_ctrl_less, ## control 
  n1 = n_mod, ## moderation
  n2 = n_ctrl ## control
)

## Output recovered proportions 
cat("Proportion of participants classified as more certain in the polarization condition (no forced choice): ", 
    round(p_pol_more, 3),
    "\n")

cat("Proportion of participants classified as less certain in the moderation condition (no forced choice): ", 
    round(p_mod_less, 3), 
    "\n")
```

## Calculate Cohen's h

Next we use p1 (polarization & moderation) and p2 (control) to calculate the effect size using: 

  h = 2 * arcsin(sqrt(p1)) - 2 * arcsin(sqrt(p2)) from @cohen1988
```{r}
library(pwr)
## Cohen's h for polarization vs control
h_pol <- ES.h(p_pol_more, p_ctrl_more)
cat("Cohen's h for polarization vs control: ", 
    round(h_pol, 3), 
    "\n")

## Cohen's h for moderation vs control  
h_mod <- ES.h(p_mod_less, p_ctrl_less)
cat("Cohen's h for moderation vs control: ", 
    round(h_mod, 3), 
    "\n")
```

## Calculate n required per group

Next, we calculate the n required per group to detect the reported effect sizes at 80% power:
```{r}
## n for polarization vs control
power_pol<- pwr.2p.test(h = h_pol, 
            sig.level = .05, 
            power = .80, 
            alternative = "greater")
cat("n per group required (polarization vs control): ", 
    ceiling(power_pol$n), 
    "\n")

## n for moderation vs control 
power_mod<- pwr.2p.test(h = h_mod,   
            sig.level = .05, 
            power = .80, 
            alternative = "greater")
cat("n per group required (moderation vs control): ", 
    ceiling(power_mod$n), 
    "\n")

```

## Calculate total N
```{r}
n_per_group <- max(ceiling(power_pol$n), 
                   ceiling(power_mod$n))

cat("Estimated N:\n")
total_N <- n_per_group * 6 ## (3 conditions x 2 forced choice)
cat("N per cell:", n_per_group, "\n")
cat("Total N: ", total_N, "\n\n")

cat("Original study:\n")
cat("Total N: ", n_pol + n_mod + n_ctrl + 54 + 48 + 53, "\n")
cat("(405 after exclusions)\n")
```





