---
title: "Figures: Jern et al. (2014) Replication"
author: "Victor Moreno"
bibliography: ../references.bib
format: html
---

## Overview 

In this notebook, I load the results, recreate Figure 9 from @jern2014, and plot participants' belief trajectories against those predicted by each of our models. All analyses are conducted in R [@R2025], following the approaches outlined in @frank2025experimentology.

## Setup
```{r}
library(tidyverse)

## Individual participants
df <- read_csv('../data/processed/JernRep-Data-Processed-Full.csv')

## Proportion of participants in each certainty class (More/Less/Equally)
df_prop_ci <- read_csv('../data/processed/JernRep-Results-Full-Proportions.csv')

## Estimated marginal means
df_emmeans <- read_csv('../data/processed/JernRep-Results-Full-MixedModel-EstMeans.csv')

## Estimated marginal means, preserving test selection
df_emmeans_choice <- read_csv('../data/processed/JernRep-Results-Full-MixedModel-EstMeans-Choice.csv')

## Choice rates across conditions
df_choice_rates <- read_csv('../data/processed/JernRep-Results-Full-ChoiceRates.csv')

## Normative model predictions
df_model <- read_csv('../data/processed/JernRep-Results-Full-ModelPredictions.csv')

## Normative model predictions, fitted to empirical priors
df_model_human <- read_csv('../data/processed/JernRep-Results-Full-ModelPredictions-HumanPrior.csv')

## Joint inference model predictions, fitted to empirical priors
df_model_joint <- read_csv('../data/processed/JernRep-Results-Full-ModelPredictions-JointInference.csv')
```
## Recreate Figure 9 from @jern2014
```{r}
## Setup
library(ggplot2)
library(scales)

## Proportion of participants in each certainty class, across conditions
df_prop_ci <- df_prop_ci |>
  mutate(CertaintyClass = factor(CertaintyClass, levels = c("Less", "Equal", "More")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))
certainty_colors <- c('#C06C84', '#6C757D', '#4F86C6')

## Plot
fig9_base_layer1 <- ggplot(df_prop_ci,
            aes(x = CertaintyClass, y = CertaintyProportion, fill = CertaintyClass)) + ## Layer by certainty class  
  ## Proportions
  geom_col(width = 0.9) +
  ## Error bars  
  geom_errorbar(aes(ymin = ci_lo, ymax = ci_hi),
                color = 'grey20',
                width = 0.12,
                linewidth = 0.5) +
  ## Specify y-axis (spread and labels)
  scale_y_continuous(limits = c(0, 1), 
                     breaks = seq(0, 1, 0.25),
                     labels = label_percent()) +
  ## Facet by condition
  facet_wrap(~Condition) +
  ## Legend
  labs(x = "", y = "Proportion of responses") +
  scale_fill_manual(values = certainty_colors, name = "Change in Certainty") + 
  guides(fill = guide_legend(title.position = "top",
    title.hjust = 0.5)) +
  ## Aesthetics
  theme_minimal() + 
  theme(plot.title = element_text(face = "bold", size = 13, margin = margin(b = 10)),
    strip.background = element_rect(fill = "grey95", color = NA),
    strip.text = element_text(face = "bold", size = 10, margin = margin(t = 6, b = 6)),
    panel.spacing = unit(1.2, "lines"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.border = element_rect(color = "grey85", fill = NA, linewidth = 0.6),
    axis.text.x = element_blank(),
    axis.title.y = element_text(
      margin = margin(r = 8)),
    axis.text = element_text(
      color = "grey30"),
    legend.position = "bottom",
    legend.text = element_text(size = 9.5),
    legend.margin = margin(t = -4),
    plot.caption = element_text(
      hjust = 0,
      size = 7.5,
      color = "grey40",
      margin = margin(t = 10)),
    plot.caption.position = "plot",
    plot.title.position = "plot"
  )

## Output
ggsave("../materials/Figures/JernRep-Results-Full-Figure-Base-Layer1.png", plot = fig9_base_layer1)
fig9_base_layer1
```
## Highlight critical comparisons visualized in Figure 9 from @jern2014 
```{r}
## Setup
library(ggplot2)
library(scales)

## Proportion of participants in each certainty class, across condition, with critical comparisons specified
df_prop_ci <- df_prop_ci %>%
  mutate(
    highlight_pair = case_when(
      Condition == "Control" & CertaintyClass == "Less" ~ "MC",
      Condition == "Moderation" & CertaintyClass == "Less" ~ "MC",
      Condition == "Control" & CertaintyClass == "More" ~ "PC",
      Condition == "Polarization" & CertaintyClass == "More" ~ "PC",
      TRUE ~ "none"
    )
  )
## Layer according to whether the bar corresponds to a critical comparison 
pair_colors <- c(MC = "#A96A99", PC = "#0072B2", none = NA)

## Plot
fig9_base_layer2 <- ggplot(df_prop_ci,
            aes(x = CertaintyClass,y = CertaintyProportion, fill = CertaintyClass, ## Layer by certainty class 
                alpha = highlight_pair != "none")) + ## Fade out non-critical bars
  ## Proportions, layered by critical comparison status
  geom_col(aes(color = highlight_pair, linewidth = highlight_pair != "none"),
           width = 0.9) +
  ## Error bars
  geom_errorbar(aes(ymin = ci_lo, ymax = ci_hi),
                color = 'grey20', 
                width = 0.12, 
                linewidth = 0.5) +
  ## Specify y-axis (spread and labels)
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25),
                     labels = label_percent()) +
  ## Facet by condition
  facet_wrap(~Condition) +
  ## Legend
  scale_alpha_manual(values = c(`TRUE` = 1, `FALSE` = 0.4), guide = "none") + ## Bold critical comparison bars, lighten others
  scale_color_manual(values = pair_colors, na.value = NA, guide = "none") + ## Create a border around critical comparison bars 
  scale_linewidth_manual(values = c(`TRUE` = 1.1, `FALSE` = 0), guide = "none") + ## Thicken critical comparison bars, weaken others
  labs(x = "", y = "Proportion of responses") +
  scale_fill_manual(values = certainty_colors, name = "Change in Certainty") +
  guides(fill = guide_legend(title.position = "top", title.hjust = 0.5)) +
  ## Aesthetics
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 13, margin = margin(b = 10)),
    strip.background = element_rect(fill = "grey95", color = NA),
    strip.text = element_text(face = "bold", size = 10, margin = margin(t = 6, b = 6)),
    panel.spacing = unit(1.2, "lines"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.border = element_rect(color = "grey85", fill = NA, linewidth = 0.6),
    axis.text.x = element_blank(),
    axis.title.y = element_text(margin = margin(r = 8)),
    axis.text = element_text(color = "grey30"),
    legend.position = "bottom",
    legend.text = element_text(size = 9.5),
    legend.margin = margin(t = -4),
    plot.caption = element_text(hjust = 0, size = 7.5, color = "grey40", margin = margin(t = 10)),
    plot.caption.position = "plot",
    plot.title.position = "plot"
  )
## Output
ggsave("../materials/Figures/JernRep-Results-Full-Figure-Base-Layer2.png", plot = fig9_base_layer2)
fig9_base_layer2
```

## Plot participants' belief trajectories across conditions against trajectories predicted by the normative model from @jern2014
```{r}
## Setup
library(ggplot2)

## Individual participants
d_long <- df |>
  pivot_longer(c(Initial, Final), names_to = "Phase", values_to = "Rating") |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))
## Estimated marginal means
df_emmeans <- df_emmeans |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))
## Normative predictions
df_model <- df_model |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))


## Plot
fig_model_comparison_layer1 <- ggplot(mapping = aes(x = Phase)) +
  ## Individual participants
  geom_line(data = d_long, aes(y = Rating, group = ResponseId), alpha = 0.05, color = "gray40", show.legend = FALSE) +
  ## Estimated marginal means with CI ribbon
  geom_ribbon(data = df_emmeans,
              aes(ymin = lower.CL, ymax = upper.CL, group = Condition),
              fill = "#3E7C91",
              alpha = 0.15) +
  ## Estimated marginal means
  geom_line(data = df_emmeans,
            aes(y = emmean, group = Condition, color = "Estimated marginal means", linetype = "Estimated marginal means"),
            linewidth = 1.3) +
  ## Normative predictions
  geom_line(data = df_model,
            aes(y = Rating, group = Condition, color = "Normative models", linetype = "Normative"),
            linewidth = 1.1) +
  ## Midpoint
  geom_hline(yintercept = 0, linetype = "dotted", color = "gray55", linewidth = 0.4) +
  ## Facet by condition
  facet_wrap(~Condition) +
  ## Legend
  scale_linetype_manual(breaks = c("Estimated marginal means", "Normative"),
    values = c(
      "Estimated marginal means" = "solid",
      "Normative" = "dashed"),
      guide = guide_legend(
        nrow = 1, 
        override.aes = list(color = c("#3E7C91", "#303030"), linewidth = 1.1))) +
  labs(x = NULL,
    y = "Certainty Rating",
    caption = "Certainty ratings range from -100 (Less Common Disease Class) to +100 (More Common Disease Class).",
    color = "",
    linetype = "") +
  scale_color_manual(
    values = c(
      "Estimated marginal means" = "#3E7C91",
      "Normative models" = "#303030"),
    guide = "none") +
  ## Specify y-axis limits to match slider scale
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, 50)) +
  ## Blow up x-axis for readability
  scale_x_discrete(expand = expansion(mult = 0.15)) +
  ## Aesthetics
  theme_minimal() +
  theme(plot.title = element_text(face = "bold", size = 13, margin = margin(b = 10)),
    strip.background = element_rect(fill = "grey95", color = NA),
    strip.text = element_text(face = "bold", size = 10, margin = margin(t = 6, b = 6)),
    panel.spacing = unit(1.2, "lines"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.border = element_rect(color = "grey85", fill = NA, linewidth = 0.6),
    axis.title.y = element_text(margin = margin(r = 8)),
    axis.text = element_text(color = "grey30"),
    legend.position = "bottom",
    legend.text = element_text(size = 9.5),
    legend.margin = margin(t = -4),
    plot.caption = element_text(hjust = 0, size = 7.5, color = "grey40",
                                 margin = margin(t = 10)),
    plot.caption.position = "plot",
    plot.title.position = "plot") 

## Output
ggsave("../materials/Figures/JernRep-Results-Full-Figure-Model-Comparison-Layer1.png", plot = fig_model_comparison_layer1)
fig_model_comparison_layer1
```

## Plot participants' trajectories in the Polarization and Moderation conditions, layering by test selection
```{r}
## Setup
library(ggplot2)

## Estimated marginal means, maintaining test selection
df_emmeans_choice <- df_emmeans_choice |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Polarization")),
         Choice = factor(Choice,
                         levels = c("Prior-consistent", "Prior-inconsistent")))

## Specify label positions
choice_labels <- df_choice_rates |>
  filter(Condition != "Control") |>
  left_join(df_emmeans_choice |> filter(Phase == "Final"),
            by = c("Condition", "Choice")) |>
  mutate(label = paste0("n = ", n), ## Create group size labels 
         Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Polarization")),
         Choice = factor(Choice, levels = c("Prior-consistent", "Prior-inconsistent")),
         ## Specify label position for each group
         nudge_y = case_when(
           Condition == "Moderation" ~ 0,
           Condition == "Polarization" & Choice == "Prior-consistent" ~ 9,
           Condition == "Polarization" & Choice == "Prior-inconsistent" ~ -9
  ))

## Plot
fig_model_test_selection <- ggplot(df_emmeans_choice,
                     aes(x = Phase, y = emmean, 
                         group = Choice, linetype = Choice)) + ## Layer by test selection
  ## Estimated marginal means 
  geom_line(linewidth = 1.3,
            position = position_dodge(width = 0.12), color = "#3E7C91",) +
  ## Error bars for each estimate
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL),
                width = 0.08, linewidth = 0.5, linetype = "solid", color = "#3E7C91",
                position = position_dodge(width = 0.12)) +
  ## End points for each estimate
  geom_point(size = 1.8, position = position_dodge(width = 0.12), color = "#3E7C91",) +
  ## Labels for each group
  geom_text(data = choice_labels,
          aes(label = label, y = emmean + nudge_y),
          hjust = -0.4, size = 3.2, show.legend = FALSE) +
  ## Midpoint line
  geom_hline(yintercept = 0, linetype = "dotted", color = "gray60") +
  ## Facet by condition
  facet_wrap(~ Condition) +
  ## Legend
  scale_linetype_manual(values = c("Prior-consistent" = "solid",
                                   "Prior-inconsistent" = "dotted"),
                        name = NULL) +
   labs(x = "", 
       y = "Certainty Rating",
       caption = "Certainty ratings range from -100 (Less Common Disease Class) to +100 (More Common Disease Class).") +
  ## Specify y-axis limits to match slider scale 
  scale_y_continuous(breaks = seq(-100, 100, 50)) +
  ## Blow up x-axis for readability 
  scale_x_discrete(expand = expansion(add = c(0.1, 0.4)))+
  coord_cartesian(ylim = c(-100, 100)) +
  ## Aesthetics
  theme_minimal() +
  theme(
        plot.title = element_text(face = "bold", size = 13, margin = margin(b = 10)),
      strip.background = element_rect(fill = "grey95", color = NA),
      strip.text = element_text(face = "bold", size = 10, margin = margin(t = 6, b = 6)),
      panel.spacing = unit(1.6, "lines"),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.border = element_rect(color = "grey85", fill = NA, linewidth = 0.6),
      axis.title.y = element_text(margin = margin(r = 8)),
      axis.text = element_text(color = "grey30"),
      legend.position = "bottom",
      legend.text = element_text(size = 9.5),
      legend.margin = margin(t = -4),
      plot.caption = element_text(hjust = 0, size = 7.5, color = "grey40",
                                 margin = margin(t = 10)),
      plot.caption.position = "plot",
      plot.title.position = "plot")

## Output
ggsave("../materials/Figures/JernRep-Results-Full-Figure-Model-TestSelection.png", plot = fig_model_test_selection)
fig_model_test_selection
```

## Plot participants' belief trajectories across conditions against trajectories predicted by the normative model fitted to empirical priors
```{r}
## Setup
library(ggplot2)
## Individual participants
d_long <- df |>
  pivot_longer(c(Initial, Final), names_to = "Phase", values_to = "Rating") |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))
## Estimated marginal means
df_emmeans <- df_emmeans |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))
## Normative predictions
df_model <- df_model |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))
## Normative predictions, fitted to empirical priors
df_model_human <-  df_model_human |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))

## Plot
fig_model_comparison_layer2 <- ggplot(mapping = aes(x = Phase)) +
  ## Individual participants
  geom_line(data = d_long, aes(y = Rating, group = ResponseId), alpha = 0.05, color = "gray40", show.legend = FALSE) +
  ## Estimated marginal means with CI ribbon
  geom_ribbon(data = df_emmeans,
              aes(ymin = lower.CL, ymax = upper.CL, group = Condition),
              fill = "#3E7C91",
              alpha = 0.15) +
  ## Estimated marginal means
  geom_line(data = df_emmeans,
            aes(y = emmean, group = Condition, color = "Estimated marginal means", linetype = "Estimated marginal means"),
            linewidth = 1.3) +
  ## Normative predictions
  geom_line(data = df_model,
            aes(y = Rating, group = Condition, color = "Normative models", linetype = "Normative"),
            linewidth = 1.1) +
  ## Normative predictions, fitted to empirical priors
  geom_line(data = df_model_human,
            aes(y = Rating, group = Condition, color = "Normative models", linetype = "Normative (empirical priors)"),
            linewidth = 1.1) +
  ## Midpoint line
  geom_hline(yintercept = 0, linetype = "dotted", color = "gray55", linewidth = 0.4) +
  ## Facet by condition
  facet_wrap(~ Condition) +
  ## Legend
  scale_linetype_manual(breaks = c("Estimated marginal means", "Normative", "Normative (empirical priors)"),
    values = c(
      "Estimated marginal means" = "solid",
      "Normative" = "dashed",
      "Normative (empirical priors)" = "dotted"),
      guide = guide_legend(
        nrow = 1, 
        override.aes = list(color = c("#3E7C91", "#303030","#303030" ), linewidth = 1.1))) +
  labs(x = NULL,
    y = "Certainty Rating",
    caption = "Certainty ratings range from -100 (Less Common Disease Class) to +100 (More Common Disease Class).",
    color = "",
    linetype = "") +
  scale_color_manual(
    values = c(
      "Estimated marginal means" = "#3E7C91",
      "Normative models" = "#303030"),
    guide = "none") +
  ## Specify y-axis limits to match slider scale 
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, 50)) +
  ## Blow up x-axis for readability
  scale_x_discrete(expand = expansion(mult = 0.15)) +
  ## Aesthetics
  theme_minimal() + 
  theme(plot.title = element_text(face = "bold", size = 13, margin = margin(b = 10)),
    strip.background = element_rect(fill = "grey95", color = NA),
    strip.text = element_text(face = "bold", size = 10, margin = margin(t = 6, b = 6)),
    panel.spacing = unit(1.2, "lines"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.border = element_rect(color = "grey85", fill = NA, linewidth = 0.6),
    axis.title.y = element_text(margin = margin(r = 8)),
    axis.text = element_text(color = "grey30"),
    legend.position = "bottom",
    legend.text = element_text(size = 9.5),
    legend.margin = margin(t = -4),
    plot.caption = element_text(hjust = 0, size = 7.5, color = "grey40",
                                 margin = margin(t = 10)),
    plot.caption.position = "plot",
    plot.title.position = "plot") 

## Output
ggsave("../materials/Figures/JernRep-Results-Full-Figure-Model-Comparison-Layer2.png", plot = fig_model_comparison_layer2)
fig_model_comparison_layer2
```
## Plot participants' belief trajectories across conditions against trajectories predicted by the joint inference model, fitted to empirical priors
```{r}
## Setup
library(ggplot2)
## Individual participants
d_long <- df |>
  pivot_longer(c(Initial, Final), names_to = "Phase", values_to = "Rating") |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))
## Estimated marginal means
df_emmeans <- df_emmeans |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))
## Normative predictions
df_model <- df_model |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))
## Normative predictions, fitted to empirical priors
df_model_human <-  df_model_human |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")))
## Joint inference predictions, fitted to empirical priors 
df_model_joint <- df_model_joint |>
  rename(Initial = Initial_slider, Final = Final_slider) |>
  pivot_longer(c(Initial, Final), names_to = "Phase", values_to = "Rating") |>
  mutate(Phase = factor(Phase, levels = c("Initial", "Final")),
         Condition = factor(Condition, levels = c("Moderation", "Control", "Polarization")),
         kappa_label = factor(paste0("Joint (κ = ", kappa, ")"),
                              levels = c("Joint (κ = 2)", "Joint (κ = 5)", "Joint (κ = 10)", "Joint (κ = 30)")))

## Plot
fig_model_comparison_layer3 <- ggplot(mapping = aes(x = Phase)) +
  ## Individual participants
  geom_line(data = d_long, aes(y = Rating, group = ResponseId), alpha = 0.05, color = "gray40", show.legend = FALSE) +
  ## Estimated marginal means with CI ribbon
  geom_ribbon(data = df_emmeans,
              aes(ymin = lower.CL, ymax = upper.CL, group = Condition),
              fill = "#3E7C91",
              alpha = 0.15) +
  ## Estimated marginal means
  geom_line(data = df_emmeans,
            aes(y = emmean, group = Condition, color = "Estimated marginal means", linetype = "Estimated marginal means"),
            linewidth = 1.3) +
  ## Normative predictions
  geom_line(data = df_model,
            aes(y = Rating, group = Condition, color = "Normative models", linetype = "Normative"),
            linewidth = 1.1) +
  ## Normative predictions, fitted to empirical priors
  geom_line(data = df_model_human,
            aes(y = Rating, group = Condition, color = "Normative models", linetype = "Normative (empirical priors)"),
            linewidth = 1.1) +
  ## Joint inference predictions, fitted to empirical priors 
  geom_line(data = df_model_joint,
            aes(y = Rating, group = interaction(Condition, kappa), color = "Joint models", linetype = kappa_label), 
            linewidth = 1.1) + 
  ## Midpoint line
  geom_hline(yintercept = 0, linetype = "dotted", color = "gray55", linewidth = 0.4) +
  ## Facet by condition
  facet_wrap(~ Condition) +
  ## Legend
  scale_linetype_manual(
    breaks =  c("Estimated marginal means", "Normative", "Normative (empirical priors)", "Joint (κ = 2)", "Joint (κ = 5)", "Joint (κ = 10)", "Joint (κ = 30)"),
    values = c(
      "Estimated marginal means" = "solid",
      "Normative" = "dashed",
      "Normative (empirical priors)" = "dotted",
      "Joint (κ = 2)" = "longdash",
      "Joint (κ = 5)" = "dotdash",
      "Joint (κ = 10)" = "twodash",
      "Joint (κ = 30)" = "dotted"),
    guide = guide_legend(nrow = 2, 
                         byrow = TRUE, 
                         override.aes = list(color = c("#3E7C91", rep("#303030",2), rep("#8B3A3A", 4)), 
                                             linewidth = 1.1))) +
  labs(x = NULL,
    y = "Certainty Rating",
    caption = "Certainty ratings range from -100 (Less Common Disease Class) to +100 (More Common Disease Class).",
    color = "",
    linetype = "") +
  scale_color_manual(
    values = c(
      "Estimated marginal means" = "#3E7C91",
      "Normative models" = "#303030",
      "Joint models" = "#8B3A3A"),
    guide = "none") +
  ## Specify y-axis limits to match slider scale 
  scale_y_continuous(limits = c(-100, 100), breaks = seq(-100, 100, 50)) +
  ## Blow up x-axis for readability
  scale_x_discrete(expand = expansion(mult = 0.15)) +
  ## Aesthetics
  theme_minimal() + 
  theme(plot.title = element_text(face = "bold", size = 13, margin = margin(b = 10)),
    strip.background = element_rect(fill = "grey95", color = NA),
    strip.text = element_text(face = "bold", size = 10, margin = margin(t = 6, b = 6)),
    panel.spacing = unit(1.2, "lines"),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.border = element_rect(color = "grey85", fill = NA, linewidth = 0.6),
    axis.title.y = element_text(margin = margin(r = 8)),
    axis.text = element_text(color = "grey30"),
    legend.position = "bottom",
    legend.text = element_text(size = 9.5),
    legend.margin = margin(t = 8),
    plot.caption = element_text(hjust = 0, size = 7.5, color = "grey40",
                                 margin = margin(t = 10)),
    plot.caption.position = "plot",
    plot.title.position = "plot") 

## Output
ggsave("../materials/Figures/JernRep-Results-Full-Figure-Model-Comparison-Layer3.png", plot = fig_model_comparison_layer3)
fig_model_comparison_layer3
```




