---
title: "Power Analysis: Jern et al. (2014) Replication"
author: "Victor Moreno"
bibliography: ../references.bib
format: html
---

## Overview

@jern2014 used a 3 (condition: polarization, moderation, control) x 2 (forced-choice groups: yes, no) between-subjects design. The primary outcome was whether participants became less certain, remained equally certain, or became more certain about their initial disease-class judgment after being presented with two contradictory test results. The primary comparisons of interest were polarization vs. control and moderation vs. control. 

In this notebook, I recover the proportions for the polarization and moderation conditions from the reported z-statistics and sample sizes, calculate Cohen's h for each comparison, and estimate the sample size required to detect these effects with 80% power [@cohen1969]. Although the original study used unequal sample sizes across cells, the present replication will allocate participants equally across the six experimental cells. Total N is therefore calculated by multiplying the required sample size per cell by 6 (3 conditions x 2 forced-choice groups). Effect sizes are estimated from the no-forced-choice group because the reported effects were smaller than those in the forced-choice group, yielding a more conservative sample size estimate. All analyses are conducted in R [@R2025], following the approaches outlined in @frank2025experimentology.

## Reported statistics
```{r}

## Reported sample sizes per condition in the no-forced-choice group
n_pol <- 87 ## polarization
n_mod <- 89 ## moderation
n_ctrl <- 86 ## control

## Reported proportions from control condition in no-forced-choice group
p_ctrl_more <- 0.20 ## proportion of participants in the control who became more certain 
p_ctrl_less <- 0.38 ## proportion of participants in the control who became less certain 
p_ctrl_equal <- 0.42 ## proportion of participants in the control who remained equally certain (not used in power analysis)

## Reported z-statistics (one-tailed z-test for proportions, no-forced-choice)
z_pol <- 2.18 ## polarization vs control, outcome = more certain 
z_mod <- 1.87 ## moderation vs control, outcome = less certain 

```

## Recover unreported proportions 

The authors reported the proportions of participants in the control condition who became less certain, remained equally certain, and became more certain. However, to estimate the sample size required to detect these effects with 80% power, we also need the corresponding outcome proportions for the polarization and moderation conditions, which were not reported.

To recover these values, we solve the equation for a one-tailed z-test for proportions, treating the reported control proportion as p~2~ and solving for the value of p~1~ (the polarization or moderation proportion) that reproduces the reported z-statistic:
$$
z = \frac{p_1 - p_2}
{\sqrt{\hat{p}(1-\hat{p})
\left(\frac{1}{n_1}+\frac{1}{n_2}\right)}}
$$

where

$$
\hat{p}=
\frac{p_1n_1+p_2n_2}{n_1+n_2}.
$$
```{r}
## Recover p1
calc_p1 <- function(z_reported, p2, n1, n2) {
  eq <- function(p1){
    ## proportion pooled across conditions 
    p_pool <- (p1 * n1 + p2 * n2) / (n1 + n2)
    ## standard error of the difference in proportions under the null
    se <- sqrt(p_pool * (1 - p_pool) * (1/n1 + 1/n2))
    ## difference between the z-statistic implied by p1 and the reported z-statistic
    ((p1-p2) / se) - z_reported
  }
  ## solve for p1 s.t the difference is 0 
  result <- uniroot(eq, 
                    interval = c(p2, 0.99))
  ## output
  return(result$root)
}

## Polarization proportion (more certain)
p_pol_more <- calc_p1(
  z_reported = z_pol,
  p2 = p_ctrl_more, ## control 
  n1 = n_pol, ## polarization
  n2 = n_ctrl ## control
)

## Moderation proportion (less certain)
p_mod_less <- calc_p1(
  z_reported = z_mod,
  p2 = p_ctrl_less, ## control 
  n1 = n_mod, ## moderation
  n2 = n_ctrl ## control
)

## Output recovered proportions 
cat("Proportion of participants classified as more certain in the polarization condition (no-forced-choice): ", 
    round(p_pol_more, 3),
    "\n")

cat("Proportion of participants classified as less certain in the moderation condition (no-forced-choice): ", 
    round(p_mod_less, 3), 
    "\n")
```

## Calculate Cohen's h

Next I use p~1~ (the polarization or moderation proportion) and p~2~ (control) to calculate Cohen's h [@cohen1988]:

$$
h = 2\arcsin\left(\sqrt{p_1}\right) - 2\arcsin\left(\sqrt{p_2}\right)
$$
Effect sizes are computed using the `pwr` package [@pwr].
```{r}
library(pwr)
## Cohen's h for polarization vs control
h_pol <- ES.h(p_pol_more, p_ctrl_more)
cat("Cohen's h for polarization vs control: ", 
    round(h_pol, 3), 
    "\n")

## Cohen's h for moderation vs control  
h_mod <- ES.h(p_mod_less, p_ctrl_less)
cat("Cohen's h for moderation vs control: ", 
    round(h_mod, 3), 
    "\n")
```

## Calculate n required per experimental cell

Next, I calculate the n required per cell to detect the reported effect sizes at 80% power:
```{r}
## n for polarization vs control
power_pol <- pwr.2p.test(h = h_pol, 
            sig.level = .05, 
            power = .80, 
            alternative = "greater")
cat("n per cell required (polarization vs control): ", 
    ceiling(power_pol$n), 
    "\n")

## n for moderation vs control 
power_mod <- pwr.2p.test(h = h_mod,   
            sig.level = .05, 
            power = .80, 
            alternative = "greater")
cat("n per cell required (moderation vs control): ", 
    ceiling(power_mod$n), 
    "\n")

```

## Estimate total N
```{r}
n_per_group <- max(ceiling(power_pol$n), 
                   ceiling(power_mod$n))
total_N <- n_per_group * 6 ## (3 conditions x 2 forced-choice groups)
cat("Estimated n per cell:", n_per_group, "\nEstimated total N: ", total_N, "\n\n")

cat("Original study:\nTotal N: ", n_pol + n_mod + n_ctrl + 54 + 48 + 53, "(405 after exclusions)\n")
```





