---
title: "Model Predictions: Jern et al. (2014) Replication"
author: "Victor Moreno"
bibliography: ../references.bib
format: html
---

## Overview

In this script, I define several functions to calculate normative belief trajectories for the experimental paradigm in @jern2014. All analyses are conducted in R [@R2025], following the approaches outlined in @frank2025experimentology.

## Define normative model

```{r}
## Setup
library(tidyverse)
## Prior over the four diseases (less common: L1, L2; more common Y1, Y2)
prior <- c(L1 = 0.01, L2 = 0.35, Y1 = 0.40, Y2 = 0.24)

## P(T = v | V = v)
test_acc <- 0.70   
test_err <- 0.10 ## totals 0.3 across the 3 remaining diseases

## Function to calculate likelihood (Polarization and Moderation conditions)
lik_disease <- function(named) {
  out <- setNames(rep(test_err, 4), names(prior))
  out[named] <- test_acc
  out}

## Function to calculate likelihood (Control condition)
lik_class <- function(named_class) {
  hi <- 0.70; lo <- 0.30
  if (named_class == "Y") c(L1 = lo, L2 = lo, Y1 = hi, Y2 = hi)
  else c(L1 = hi, L2 = hi, Y1 = lo, Y2 = lo)}

## Function to calculate posteriors 
posterior <- function(lik1, lik2) {
  unnorm <- prior * lik1 * lik2 ## Calculate raw posterior
  post <- unnorm / sum(unnorm) ## Normalize
  sum(post[c("Y1", "Y2")])} ## Collapse to the more common class


## Pooled prior
p_prior <- sum(prior[c("Y1", "Y2")])

## Define predictions 
predictions <- tribble(
  ~Condition, ~p_posterior,
  "Polarization", posterior(lik_disease("Y1"), lik_disease("L1")),
  "Moderation", posterior(lik_disease("Y2"), lik_disease("L2")),
  "Control", posterior(lik_class("Y"), lik_class("L"))) |>
  mutate(p_prior = p_prior,
         Initial = 200 * p_prior - 100, ## Convert to slider scale 
         Final = 200 * p_posterior - 100)

## Export
modelpredictions <- predictions |>
  pivot_longer(c(Initial, Final), names_to = "Phase", values_to = "Rating") |>
  select(Condition, Phase, Rating)
write_csv(modelpredictions, "../data/processed/JernRep-Results-Full-ModelPredictions.csv")
```

## Define normative model, initialized with participants' actual priors

```{r}
## Set up
df_emmeans <- read_csv('../data/processed/JernRep-Results-Full-MixedModel-EstMeans.csv')

## Pull participants' priors from the emmeans file and convert them to probability scale  
obs_human <- df_emmeans |>
  filter(Phase == "Initial") |>
  mutate(p_obs = (emmean + 100) / 200) |>
  select(Condition, p_obs)

## Unpack participants' priors across the four diseases (emmeans is aggregated across disease classes)
prior_human <- function(p_obs) {
  c(prior[c("L1", "L2")] * (1 - p_obs) / (1 - p_prior),
    prior[c("Y1", "Y2")] * p_obs / p_prior)}

## Function to calculate posterior
posterior_human <- function(lik1, lik2, prior_vec = prior) {
  unnorm <- prior_vec * lik1 * lik2  ## Calculate raw posterior
  post   <- unnorm / sum(unnorm) ## Normalize 
  sum(post[c("Y1", "Y2")])} ## Collapse to the more common class


## Define predictions
predictions_human <- obs_human |>
  rowwise() |>
  mutate(p_posterior = case_when(
    Condition == "Polarization" ~ posterior_human(lik_disease("Y1"), lik_disease("L1"), prior_human(p_obs)),
    Condition == "Moderation"~ posterior_human(lik_disease("Y2"), lik_disease("L2"), prior_human(p_obs)),
    Condition == "Control" ~ posterior_human(lik_class("Y"), lik_class("L"), prior_human(p_obs)))) |>
  ungroup() |>
  mutate(Initial = 200 * p_obs - 100, ## Convert to slider scale
         Final = 200 * p_posterior - 100)


## Export
modelpredictions_human <- predictions_human |>
  pivot_longer(c(Initial, Final), names_to = "Phase", values_to = "Rating") |>
  select(Condition, Phase, Rating)
write_csv(modelpredictions_human, "../data/processed/JernRep-Results-Full-ModelPredictions-HumanPrior.csv")

```

## Define joint-inference model

```{r}
## Set up
df_emmeans <- read_csv('../data/processed/JernRep-Results-Full-MixedModel-EstMeans.csv')

## Pull participants' priors from the emmeans file and convert them to probability scale  
obs_human <- df_emmeans |>
  filter(Phase == "Initial") |>
  mutate(p_obs = (emmean + 100) / 200) |> ## Convert from slider to probability scale 
  select(Condition, p_obs)

## Unpack participants' priors across the four diseases (emmeans is aggregated across disease classes)
prior_human <- function(p_obs) {
  c(prior[c("L1", "L2")] * (1 - p_obs) / (1 - p_prior),
    prior[c("Y1", "Y2")] * p_obs / p_prior)}

## Function to calculate likelihood (Polarization and Moderation conditions)
lik_disease_joint <- function(named, acc = 0.7) { 
  out <- setNames(rep((1-acc)/3, 4), names(prior))
  out[named] <- acc
  out}

## Function to calculate likelihood (Control condition)
lik_class_joint <- function(named_class, acc = 0.7) {
  hi <- acc; lo <- (1-acc)
  if (named_class == "Y") c(L1 = lo, L2 = lo, Y1 = hi, Y2 = hi)
  else c(L1 = hi, L2 = hi, Y1 = lo, Y2 = lo)}

## Function to calculate posterior
posterior_joint <- function(lik1, lik2, prior_vec = prior) {
  unnorm <- prior_vec * lik1 * lik2  ## Calculate raw posterior
  post <- unnorm / sum(unnorm) ## Normalize 
  sum(post[c("Y1", "Y2")])} ## Collapse to the more common class


## Specify test sequences across conditions  
condition_tests <- list(
  Polarization = function(acc) list(lik_disease_joint("Y1", acc), lik_disease_joint("L1", acc)),
  Moderation = function(acc) list(lik_disease_joint("Y2", acc), lik_disease_joint("L2", acc)),
  Control = function(acc) list(lik_class_joint("Y", acc), lik_class_joint("L", acc)))

## Grid of possible values of participants' beliefs about test reliability 
rel_grid <- seq(0.001, 0.999, length.out = 2000)

## Function to infer a posterior over theta from the observed test pair, then return P(H | tests) marginalized over theta
predict_joint <- function(condition, kappa, prior_vec) {
  theta_prior <- dbeta(rel_grid, 0.7 * kappa, 0.3 * kappa) ## Kappa represents the prior certainty about theta (centered around 0.7) instilled by instructions provided to participants
  theta_prior <- theta_prior / sum(theta_prior)
  
  ## Marginal likelihood of the observed test pair at each candidate value for theta (i.e given a fixed test reliability, how likely are these two results, averaging across all candidate diseases?)
  ml <- sapply(rel_grid, function(acc) {     
    liks <- condition_tests[[condition]](acc) ## Likelihoods of each observed test result given each disease, at this theta value
    sum(prior_vec * liks[[1]] * liks[[2]])}) ## Calculate the sum of P(D) x P(t1 | D, theta) x P(t2 | D, theta) across all values of D
  
  ## Calculate the posterior over theta 
  theta_post <- ml * theta_prior / sum(ml * theta_prior) 
  
  ## Calculate P(H | tests, theta) at each candidate theta, to be averaged over theta's posterior below, giving us P(H | tests)
  p_by_theta <- sapply(rel_grid, function(acc) {
    liks <- condition_tests[[condition]](acc)
    posterior_joint(liks[[1]], liks[[2]], prior_vec)})
  
  ## Marginalize over theta by taking the average P(H | tests, theta) across candidates, weighted by theta's posterior
  list(
    prediction = sum(theta_post * p_by_theta),
    theta_post = theta_post)}

## Specify kappas to generate predictions 
kappa_grid <- c(2, 5, 10, 30)
## Initialize empty data frame
predicted_finals <- data.frame()
## Initialize empty list 
theta_posts_joint <- list()

## Looping through each condition
for (cond in obs_human$Condition) {
  ## Pull the est. marginal mean of participants' priors (already converted to probability scale) 
  p_obs_val <- obs_human$p_obs[obs_human$Condition == cond]
  ## Unpack participants' priors across the four diseases
  prior_vec <- prior_human(p_obs_val)
  
  ## For each kappa value in our grid
  for (kappa in kappa_grid) {
    ## Run the joint inference model and save the predicted posterior (Final belief)
    result <- predict_joint(cond, kappa, prior_vec)
    
    ## Now, append these rows to our predicted_finals data frame (initialized above)
    predicted_finals <- rbind(predicted_finals, data.frame(
      Condition = cond, ## Specify condition
      kappa = kappa, ## Specify kappa
      Initial_slider = 200 * p_obs_val - 100, ## Convert Initial belief to slider scale
      Final_slider = 200 * result$prediction - 100 ## Convert Final belief to slider scale
    ))
    theta_posts_joint[[paste(cond, kappa, sep = "_")]] <- result$theta_post  ## Extra posterior beliefs over theta
  }
}

## Export
write_csv(predicted_finals, "../data/processed/JernRep-Results-Full-ModelPredictions-JointInference.csv")
```

## Define joint-inference model, initialized with an uninformed prior over test reliability

```{r}
## Set up
df_emmeans <- read_csv('../data/processed/JernRep-Results-Full-MixedModel-EstMeans.csv')

## Pull participants' priors from the emmeans file and convert them to probability scale  
obs_human <- df_emmeans |>
  filter(Phase == "Initial") |>
  mutate(p_obs = (emmean + 100) / 200) |> ## Convert from slider to probability scale 
  select(Condition, p_obs)

## Unpack participants' priors across the four diseases (emmeans is aggregated across disease classes)
prior_human <- function(p_obs) {
  c(prior[c("L1", "L2")] * (1 - p_obs) / (1 - p_prior),
    prior[c("Y1", "Y2")] * p_obs / p_prior)}

## Function to calculate likelihood (Polarization and Moderation conditions)
lik_disease_joint <- function(named, acc = 0.7) { 
  out <- setNames(rep((1-acc)/3, 4), names(prior))
  out[named] <- acc
  out}

## Function to calculate likelihood (Control condition)
lik_class_joint <- function(named_class, acc = 0.7) {
  hi <- acc; lo <- (1-acc)
  if (named_class == "Y") c(L1 = lo, L2 = lo, Y1 = hi, Y2 = hi)
  else c(L1 = hi, L2 = hi, Y1 = lo, Y2 = lo)}

## Function to calculate posterior
posterior_joint <- function(lik1, lik2, prior_vec = prior) {
  unnorm <- prior_vec * lik1 * lik2  ## Calculate raw posterior
  post <- unnorm / sum(unnorm) ## Normalize 
  sum(post[c("Y1", "Y2")])} ## Collapse to the more common class

## Specify test sequences across conditions  
condition_tests <- list(
  Polarization = function(acc) list(lik_disease_joint("Y1", acc), lik_disease_joint("L1", acc)),
  Moderation = function(acc) list(lik_disease_joint("Y2", acc), lik_disease_joint("L2", acc)),
  Control = function(acc) list(lik_class_joint("Y", acc), lik_class_joint("L", acc)))

## Grid of possible values of participants' beliefs about test reliability 
rel_grid <- seq(0.001, 0.999, length.out = 2000)

## Function to infer a posterior over theta from the observed test pair, then return P(H | tests) marginalized over theta
predict_joint_uninformative <- function(condition, prior_vec) {
  theta_prior <- dbeta(rel_grid, 1, 1) ## Uniform distribution of priors over theta 
  theta_prior <- theta_prior / sum(theta_prior)
  
  ## Marginal likelihood of the observed test pair at each candidate value for theta (i.e given a fixed test reliability, how likely are these two results, averaging across all candidate diseases?)
  ml <- sapply(rel_grid, function(acc) {     
    liks <- condition_tests[[condition]](acc) ## Likelihoods of each observed test result given each disease, at this theta value
    sum(prior_vec * liks[[1]] * liks[[2]])}) ## Calculate the sum of P(D) x P(t1 | D, theta) x P(t2 | D, theta) across all values of D
  
  ## Calculate the posterior over theta 
  theta_post <- ml * theta_prior / sum(ml * theta_prior) 
  
  ## Calculate P(H | tests, theta) at each candidate theta, to be averaged over theta's posterior below, giving us P(H | tests)
  p_by_theta <- sapply(rel_grid, function(acc) {
    liks <- condition_tests[[condition]](acc)
    posterior_joint(liks[[1]], liks[[2]], prior_vec)})
  
  ## Marginalize over theta by taking the average P(H | tests, theta) across candidates, weighted by theta's posterior
  list(
    prediction = sum(theta_post * p_by_theta),
    theta_post = theta_post)}

## Initialize empty data frame
predicted_finals_uninformed <- data.frame()
## Initialize empty list
theta_posts_uninformed <- list()

## Looping through each condition
for (cond in obs_human$Condition) {
  ## Pull the est. marginal mean of participants' priors (already converted to probability scale) 
  p_obs_val <- obs_human$p_obs[obs_human$Condition == cond]
  ## Unpack participants' priors across the four diseases
  prior_vec <- prior_human(p_obs_val)
  result <- predict_joint_uninformative(cond, prior_vec)
  ## Now, append these rows to our predicted_finals data frame (initialized above)
  predicted_finals_uninformed <- rbind(predicted_finals_uninformed, data.frame(
    Condition = cond, ## Specify condition
    Initial_slider = 200 * p_obs_val - 100, ## Convert Initial belief to slider scale
    Final_slider = 200 * result$prediction - 100 ## Convert Final belief to slider scale
    ))
  theta_posts_uninformed[[cond]] <- result$theta_post ## Extra posterior beliefs over theta 
}

## Export
write_csv(predicted_finals_uninformed, "../data/processed/JernRep-Results-Full-ModelPredictions-JointInferenceUninformed.csv")

```
